Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-09-17 docs/comments/comments.tex
minor fix based on Mike's comment
some changes in the 1st comment of the 1st reviewer

\noindent
{\bf Response:}
Indeed,
an application firewall is actually a defense
mechanism that fits in our study.
Besides,
in reference~\cite{DPJV06}
the authors indicate three mechanisms~\cite{BK04,PB05,HO05b}
that we include in our study as
application firewalls.
Such mechanisms though,
can be seen as host-based application firewalls
which are different from the network-based
application firewalls.
Mechanisms coming from the later category
operate directly at the application
layer of the protocol stack and
in most cases they are modules
of the web server
(e.g. {\tt modsecurity})\footnote{\url{https://www.modsecurity.org/}}.
Even though we do not include such mechanisms
(note also that {\tt modsecurity} is
not a research approach),
they can be analyzed based on our criteria.\\
% note: I do not know if we must update the text
% of the paper to address the above comment.

>>>>

\noindent
{\bf Response:}
In general,
a way to check if a mechanism can be examined
based on our criteria,
is to see if and how it fits into our
exploitation model (point of detection).
Specifically,
application firewalls
fit into our study.
Besides,
in reference~\cite{DPJV06}
the authors indicate three mechanisms~\cite{BK04,PB05,HO05b}
that we include in our analysis as
application firewalls.\\

% Such mechanisms though,
% can be seen as host-based application firewalls
% which are different from the network-based
% application firewalls.
% Mechanisms coming from the later category
% operate directly at the application
% layer of the protocol stack and
% in most cases they are modules
% of the web server
% (e.g. {\tt modsecurity})\footnote{\url{https://www.modsecurity.org/}}.
% Even though we do not include such mechanisms
% in our study,
% they can be analyzed based on our criteria.\\
% note: I do not know if we must update the text
% of the paper to address the above comment.
